---
title: 'Build dataset from Enron mail one'
date: 'September 9, 2022'
author: 'Maurizio P. De Marchi'
output:
html_document:
df_print: paged
theme: readable
toc: true
toc_float: true
pdf_document: default
editor_options:
chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      tidy.opts = list(width.cutoff = 60),
                      tidy = TRUE)
library(tidyverse)
library(stringi)
```

First, we need to understand the structure.
Each folder corresponds to a person.
Files are divided in the following categories: all documents, contacts, deleted items, discussion threads, inbox, notes inbox , sent
```{r}
enron_root_dir <- "datasets/non-scam/enron"

```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
