---
title: 'Build dataset from Enron mail one'
date: 'September 1, 2022'
author: 'Maurizio P. De Marchi'
output:
html_document:
df_print: paged
theme: readable
toc: true
toc_float: true
pdf_document: default
editor_options:
chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      tidy.opts = list(width.cutoff = 60),
                      tidy = TRUE)
library(tidyverse)
library(stringi)
```

First, we need to understand the structure.
Each folder corresponds to a person.
Files are divided in too many and too diverse categories.

Given the scope of the project, we are interested only in the sent mail, because we can be sure about the legitimacy. We also want to have a similar structure with respect to the scam dataset, so we will only fetch sender, date, subject and text

```{r}
enron_root_dir <- "datasets/non-scam/enron"
# To look for:
#   Date:
#   From:
#   Subject:
#   Text (one empty line after X-FileName:)

directories <- list.dirs(path = enron_root_dir, full.names = TRUE, recursive = FALSE) # we only want the first one


df <- data.frame(From='', Date='', Subject='', Text='')

# triggers
date_trigger <- "Date:"
from_trigger <- "From:"
subject_trigger <- "Subject:"
text_trigger <- "X-FileName:" # email text start after this line


```

```{r}
# set current directories
directories <- list.dirs(path = enron_root_dir, full.names = TRUE, recursive = FALSE) # we only want the first one

# directories <- paste0(directories, "/_sent_mail/")
# save_name <- "datasets/pre-processed/non-scam-enron_sent_mail.csv"

directories <- paste0(directories, "/personal/")
save_name <- "datasets/pre-processed/non-scam-enron_personal.csv"

```
Actual building
```{r}
for(directory in directories)
{
  emails <- list.files(directory, full.names = TRUE, recursive = TRUE)
  for (email in emails)
  {
    from <- ''
    date <- ''
    subject <- ''
    text <- ''

    text_started <- FALSE # email text has started

    # open file connection
    if (is.null(email)) {next}
    file_connection <- file(description = email, open = "r", blocking = TRUE)
    # Loop till the line is the empty vector, character(0).
    repeat
    {
      pl <- readLines(file_connection, n = 1) # Read one line from the connection
      if (length(pl) == 0) { break } # If the line is empty, exit.

      # Get the first 3
      if (!text_started) {
        if (str_detect(string = pl, pattern = paste0("(?<!.)",from_trigger, "(.*?)"))) {
          from <- str_replace(string = pl, pattern = fixed(from_trigger), replacement = '')
        }
        else {
          if (str_detect(string = pl, pattern = paste0("(?<!.)",date_trigger,"(.*?)"))) {
            date <- str_replace(string = pl, pattern = fixed(date_trigger), replacement = '')
          }
          else {
            if (str_detect(string = pl, pattern = paste0("(?<!.)",subject_trigger,"(.*?)"))) {
              subject <- str_replace(string = pl, pattern = fixed(subject_trigger), replacement = '')
            }
          }
        }
      }
      else {
        text <- paste(text, pl, sep = '\n')
        next
      }
      if (str_detect(string = pl, pattern = fixed(text_trigger))) {
        text_started <- TRUE
      }
    }
    # Explicitly opened connection needs to be explicitly closed.
    close(file_connection)
    rm(file_connection) # Removes the connection object from memory.

    df <- rbind(df, data.frame(From = from, Date = date, Subject = subject, Text = text))
  }
  write.csv(df, file = paste("datasets/non-scam/tmp/temp.csv"))
}
write.csv(df, file = save_name)
```
